Appendix B: R Functions for Design Analysis with Pearson Correlation

### 2020-05-04 Documents/Appendix_B/Appendix_B.Rmd
Appendix B corrige

---
title: "Appendix B: R Functions for Design Analysis Pearson Correlation"
author: 
date:
bibliography: MS_rho.bib 
cls: apa.csl
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

@@

- `pro_r()` for prospective design analysis. Given the hypothetical population correlation value and the required power level, this function performs a prospective design analysis according to the defined alternative hypothesis and significance level. The required sample size is computed together with the associated Type-M error, Type-S error, and the minimum correlation value that would result significant. 
```{r, eval=FALSE}
pro_r(rho, power = .80, alternative = c("two.sided", "less", "greater"), 
      sig_level = .05, range_n = c(1,1000), B = 1e4, tol = .005, 
      display_message = TRUE, seed = NULL)
```

@@

## Examples code

>>>>

---
title: "Appendix B: R Functions for Design Analysis with Pearson Correlation"
author: 
date:
bibliography: Appendix_B.bib 
cls: apa.csl
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

@@

- `pro_r()` for prospective design analysis. Given the hypothetical population correlation value and the required power level, this function performs a prospective design analysis according to the defined alternative hypothesis and significance level. The required sample size is computed together with the associated Type-M error, Type-S error, and the minimum correlation value that would result significant. 
```{r, eval=FALSE}
pro_r(rho, power = .80, alternative = c("two.sided", "less", "greater"), 
      sig_level = .05, range_n = c(1,1000), B = 1e4, tol = .01, 
      display_message = TRUE, seed = NULL)
```

@@
